---
title: "Data Wrangling and Modeling"
---

## Packages Used In This Analysis

```{r}
#| label: load packages
#| message: false
#| warning: false

library(GGally)
library(tidyverse)
library(tidyclust)
library(broom)
library(mclust)
library(tidymodels)
library(dplyr)
library(ggplot2)
```

GGally to get the ggpairs function
tidyclust to specify clustering models
Broom to Convert Statistical Objects into Tidy Tibbles
mclust for model based clustering
dplyr to massage and summarize data
tidymodels for modeling
tidyverse for piping and altering data
ggplot2 for graphs in eda and clustering

## Data Description

```{r}
#| label: import data
#| warning: false
vgsales <- readr::read_csv("C:/Users/19493/Desktop/vgsales.csv")
```

I got the dataset from a site called Kaggle.com and the data set analyzes sales data from over 16,000 games that had more than 100,000 global sales. The data itself was generated by a scrape of vgchartz.com, which is another website that goes into deep analysis about video games sales.

The Data has 11 different variables Rank is a games placement in sales, Name is the name of the game, Platform is which console said game came out on, Genre is the genre of the game, Publisher is who published the game, and the different Sales columns relate to how many copies the game sole in North America, Europe, Japan, all other territories, and final how many total copies were sold globally.


```{r}
vgsales <- vgsales %>%
  filter(Global_Sales > 1) %>%
  mutate(log_sales = log(Global_Sales))
```

```{r}
ggplot(data = vgsales,
       aes(x = Year, y = Global_Sales)) + geom_boxplot()
```


```{r}
ggplot(data = vgsales,
       aes(x = Year, y = log_sales)) + geom_boxplot()
```
